---
title: "CS 1675 Final Project"
subtitle: "Example: save and reload a model object"
author: "Graham Zug"
output: html_document
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 0: Setting The Workspace Up

This part is just loading in packages and data, as well as splitting the data up logically (e.g. dividing the response 1 from the response 2 inputs).



Separate the variables associated with the Option B classification formulation. Notice that the `outcome_2` variable is converted to a factor with a specific ordering of the levels. Use this ordering when modeling in `caret` to make sure everyone predicts the `Fail` class as the "positive" class in the confusion matrix.  

```{r, make_step_2_option_b_data, eval=TRUE}
step_2_b_df <- df %>% select(xA, xB, response_1, x07:x11, outcome_2) %>% 
  mutate(outcome_2 = factor(outcome_2, levels = c("Fail", "Pass")))
```

Separate the variables associated with the Option A classification formulation. The `outcome_2` variable is again converted to a factor with a specific ordering of the levels.  

```{r, make_step_2_option_a_data, eval=TRUE}
step_2_a_df <- df %>% select(xA, xB, x01:x11, outcome_2) %>% 
  mutate(outcome_2 = factor(outcome_2, levels = c("Fail", "Pass")))
```


## Load packages

```{r, load_packages, eval=TRUE}
library(caret)
library(tidyverse)
library(rstanarm)
library(dotwhisker)
library(broom.mixed)
library(dplyr)
library(ggplot2)
library(e1071)
library(neuralnet)
library(plotROC)
```



```{r, controls, eval=TRUE}

my_ctrl_2 <- trainControl(method = "repeatedcv", 
                             number = 5,
                             repeats = 10,
                             summaryFunction = twoClassSummary,                          
                             classProbs = TRUE,
                             savePredictions = TRUE)
```




##Part 3: Binary Classification Option A (Accuracy)

Time to fit some regression models to predict outcome2!

```{r, lm_models_02, eval=TRUE}
metric_2 = "AUC"
```


```{r, glm_models_02, eval=TRUE}
glm_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "glm",
                        preProcess = c("center","scale"),
                        metric = metric_2,
                        trControl = my_ctrl_2)
glm_mod_step_2
```


```{r, glmnet_models_2, eval=TRUE}
glmnet_mod_step_2 <- train(outcome_2 ~ . + .*. + .*.*., data = step_2_b_df,
                        method = "glmnet",
                        preProcess = c("center","scale"),
                        metric = metric_2,
                        trControl = my_ctrl_2)
glmnet_mod_step_2
```

```{r, neural_network_2, eval=TRUE}
nnet_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "nnet",
                        metric = metric_2,
                        hidden = 8,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        trace = FALSE)

nnet_mod_step_2
```

```{r, forest_2, eval=TRUE}
forest_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "rf",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)

forest_mod_step_2
```

```{r, gradient_boosted_tree_02, include = FALSE, eval=TRUE}
grad_tree_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "xgbTree",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)
```

```{r, gradient_boosted_tree_2, eval = FALSE}
grad_tree_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "xgbTree",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)
```

```{r,special_block_2, eval=TRUE}
grad_tree_mod_step_2
```

```{r, k_nearest_neighbors_2, eval=TRUE}
knn_mod_step_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "knn",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2)

knn_mod_step_2
```

```{r, partial_least_squares_2, eval=TRUE}
partial_least_squares_2 <- train(outcome_2 ~ ., 
                        data = step_2_b_df,
                        method = "pls",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2)

partial_least_squares_2
```


#Part 4: Binary Classification Option B (Accuracy)

```{r, glm_models_03, eval=TRUE}
glm_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "glm",
                        preProcess = c("center","scale"),
                        metric = metric_2,
                        trControl = my_ctrl_2)
glm_mod_step_3
```


```{r, glmnet_models_3, eval=TRUE}
glmnet_mod_step_3 <- train(outcome_2 ~ . + .*. + .*.*., data = step_2_a_df,
                        method = "glmnet",
                        preProcess = c("center","scale"),
                        metric = metric_2,
                        trControl = my_ctrl_2)
glmnet_mod_step_3
```

```{r, neural_network_3, eval=TRUE}
nnet_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "nnet",
                        metric = metric_2,
                        hidden = 8,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        trace = FALSE)

nnet_mod_step_3
```

```{r, forest_3, eval=TRUE}
forest_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "rf",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)

forest_mod_step_3
```

```{r, gradient_boosted_tree_03, include = FALSE, eval=TRUE}
grad_tree_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "xgbTree",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)
```

```{r, gradient_boosted_tree_3, eval = FALSE}
grad_tree_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "xgbTree",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2,
                        importance = TRUE)
```

```{r,special_block_3, eval=TRUE}
grad_tree_mod_step_3
```

```{r, k_nearest_neighbors_3, eval=TRUE}
knn_mod_step_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "knn",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2)

knn_mod_step_3
```

```{r, partial_least_squares_3, eval=TRUE}
partial_least_squares_3 <- train(outcome_2 ~ ., 
                        data = step_2_a_df,
                        method = "pls",
                        metric = metric_2,
                        preProcess = c("center","scale"),
                        trControl = my_ctrl_2)

partial_least_squares_3
```






